Bullet Data Preparation for LIME Diagnostics Paper

### 2020-09-14 code/data-preparation.Rmd
small changes

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

@@

@@

```{r}
library(cowplot)
library(dplyr)
library(ggplot2)
library(randomForest)
library(stringr)
library(tidyr)
```

@@

Create a new version of the data with the land IDs separated into separate variables for an analysis of the number of observations in this data:

```{r}
bullet_train_raw_expanded <-
  bullet_train_raw %>%
  separate(land_id1,
           sep = "-",
           into = c("study1", "barrel1", "bullet1", "land1")) %>%
  separate(land_id2,
           sep = "-",
           into = c("study2", "barrel2", "bullet2", "land2"))
```

@@

@@

@@

```{r}
write.csv(
  x = bullet_train, 
  file = "../data/bullet-train.csv", 
  row.names = FALSE
)
```

@@

```{r}
zip(
  zipfile = "../data/raw/hamby-comparisons.csv.zip", 
  files = "../data/raw/hamby-comparisons.csv"
)
zip(
  zipfile = "../data/bullet-train.csv.zip", 
  files = "../data/bullet-train.csv"
)
```

@@

```{r}
write.csv(
  x = hamby224_test, 
  file = "../data/bullet-test.csv", 
  row.names = FALSE
)
```

@@

```{r}
zip(
  zipfile = "../data/raw/h224-set1-features.rds.zip", 
  files = "../data/raw/h224-set1-features.rds"
)
zip(
  zipfile = "../data/raw/h224-set11-features.rds.zip", 
  files = "../data/raw/h224-set11-features.rds"
)
zip(
  zipfile = "../data/bullet-test.csv.zip", 
  files = "../data/bullet-test.csv"
)
```

@@

```{r}
write.csv(
  x = signatures_trimmed,
  file = "../data/example-signatures.csv",
  row.names = FALSE
)
```

@@

```{r}
zip(
  zipfile = "../data/raw/signatures.rds.zip", 
  files = "../data/raw/signatures.rds"
)
zip(
  zipfile = "../data/example-signatures.csv.zip", 
  files = "../data/example-signatures.csv"
)
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, fig.align = "center")
```

@@

**NOTE** The code chunks where the prepared data versions are shared have `eval = FALSE`. These code chunks must be run manually. This is done to help avoid any accidental changes of the data.

@@

```{r}
library(cowplot)
library(dplyr)
library(forcats)
library(ggplot2)
library(randomForest)
library(stringr)
library(tidyr)
```

@@

Create a new version of the data with the land IDs separated into separate variables for an analysis of the number of observations in this data and reorder the barrels:

```{r}
bullet_train_raw_expanded <-
  bullet_train_raw %>%
  separate(land_id1,
           sep = "-",
           into = c("study1", "barrel1", "bullet1", "land1")) %>%
  separate(land_id2,
           sep = "-",
           into = c("study2", "barrel2", "bullet2", "land2")) %>%
  mutate(barrel1 = fct_relevel(barrel1, paste0("Br", 1:10), "BrUnk"),
         barrel2 = fct_relevel(barrel2, paste0("Br", 1:10), "BrUnk"))
```

@@

## Compare Dimensions to rtrees

@@

**XXX Need to determine why the number of dimensions do not match. XXX**

## Preparing Data

@@

```{r eval = FALSE}
write.csv(
  x = bullet_train, 
  file = "../data/bullet-train.csv", 
  row.names = FALSE
)
```

@@

```{r eval = FALSE}
zip(
  zipfile = "../data/raw/hamby-comparisons.csv.zip", 
  files = "../data/raw/hamby-comparisons.csv"
)
zip(
  zipfile = "../data/bullet-train.csv.zip", 
  files = "../data/bullet-train.csv"
)
```

@@

```{r eval = FALSE}
write.csv(
  x = hamby224_test, 
  file = "../data/bullet-test.csv", 
  row.names = FALSE
)
```

@@

```{r eval = FALSE}
zip(
  zipfile = "../data/raw/h224-set1-features.rds.zip", 
  files = "../data/raw/h224-set1-features.rds"
)
zip(
  zipfile = "../data/raw/h224-set11-features.rds.zip", 
  files = "../data/raw/h224-set11-features.rds"
)
zip(
  zipfile = "../data/bullet-test.csv.zip", 
  files = "../data/bullet-test.csv"
)
```

@@

```{r eval = FALSE}
write.csv(
  x = signatures_trimmed,
  file = "../data/example-signatures.csv",
  row.names = FALSE
)
```

@@

```{r eval = FALSE}
zip(
  zipfile = "../data/raw/signatures.rds.zip", 
  files = "../data/raw/signatures.rds"
)
zip(
  zipfile = "../data/example-signatures.csv.zip", 
  files = "../data/example-signatures.csv"
)
```
